---
title: "Predicting_Credit_Rating"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tree)
library(rpart)
library(rpart.plot)
library(caret)
library(e1071)
library(randomForest)

```




## Function to convert to factors
```{r}

to.factors = function(credit, variables){
  for (variable in variables) {
    credit[variable] = as.factor(credit[[variable]])
    
  }
  return(credit)
}

```


```{r}

credit = read.csv("D://credit.csv",header = T,sep = ",")
dim(credit)
```

# Data Availibility
```{r}
x=c()
for(i in 1:ncol(credit))
{
  nulls_count=length(which(is.na(credit[i])))
  x=append(x,nulls_count)
  print(nulls_count)
}
```

```{r}
x=c()
num.na=colSums(is.na(credit))
num.na

num.na=colSums(!is.na(credit))*100/nrow(credit)
num.na
```

## Converting variables to factors
```{r}

categorical.vars=c("credit.rating","account.balance","previous.credit.payment.status",
                   "credit.purpose","savings","employment.duration","installment.rate",
                   "marital.status","guarantor","residence.duration",
                   "current.assets","other.credits","apartment.type","bank.credits",
                   "occupation","dependents","telephone","foreign.worker")

credit=to.factors(credit, categorical.vars)

```

Creating training and test data
```{r}
indexes=sample(1:nrow(credit),size = 0.7*nrow(credit))

train.data=credit[indexes,]

test.data=credit[-indexes,]

```

## Building a Random forest Model
```{r}
formula.init="credit.rating~."
formula.init=as.formula(formula.init)
formula.init




rf.model=randomForest(formula.init,data=train.data,
                      importance = T,proximity = T)


rf.model
```

## Predicting the Credit Rating of the test data
```{r}
test.feature.vars=test.data[,-1]
test.class.vars=test.data[,1]




rf.predictions=predict(rf.model,test.feature.vars,
                       type="class")
rf.predictions
```

## Confusion Matrix to check the accuracy of our model
```{r}
confusionMatrix(data=rf.predictions,reference = test.class.vars,
                positive = "1")

```


## Parameter tuning for our model
```{r}
nodesize.vals = c(2,3,4,5)
ntree.vals = c(200, 500, 1000, 2000)
tuning.results = tune.randomForest(formula.init,
                                   data = train.data,
                                   mtry = 3,
                                   nodesize = nodesize.vals,
                                   ntree = ntree.vals)
print(tuning.results)


```

## important variables for our model
```{r}
rf.model$importance
```

## Buiding a model with the important variables
```{r}
formula.new="credit.rating~account.balance, previous.credit.payment.status,
marital.status, apartment.type"
formula.new=as.formula(formula.init)
formula.new

rf.model.best = tuning.results$best.model
rf.predictions.best = predict(rf.model.best, test.feature.vars,
                              type = "class")


```


## Confusion matrix for our tuned model
```{r}
confusionMatrix(data=rf.predictions.best,
                reference = test.class.vars, positive = "1")


```


